`r region$Name`

### 2020-05-28 code/index.Rmd
Add per region landing page

```{r}
regions_dft = readRDS("regions_dft.Rds")
regions_dft_centroids = sf::st_point_on_surface(regions_dft)
regions_dft$html_name = tolower(gsub(pattern = " |, ", replacement = "-", regions_dft$Name))
regions_dft$url = paste0("<a href='", regions_dft$html_name ,"' target='_blank'>", regions_dft$html_name, "</a>")
```

```{r}
pvars = c("Name", "Level")
tm_shape(regions_dft) + tm_polygons("Level", popup.vars = pvars) + tm_shape(regions_dft_centroids) + tm_text("Name", size = 0.7)
```

```{r}
regions_dft %>%
  sf::st_drop_geometry() %>%
  select(Name, Level, url) %>% 
  arrange(Name) %>% 
  DT::datatable(escape = -4)
```

>>>>

```{r, eval=FALSE}
# test build works before running for all:
source("code/build.R")
```

```{r}
regions = readRDS("regions_dft.Rds")
regions_centroids = sf::st_point_on_surface(regions)
regions$html_name = tolower(gsub(pattern = " |, ", replacement = "-", regions$Name))
regions$url = paste0("<a href='", regions$html_name ,"' target='_blank'>", regions$Name, "</a>")
```

```{r}
pvars = c("Name", "Level")
tm_shape(regions) + tm_polygons("Level", popup.vars = pvars) + tm_shape(regions_centroids) + tm_text("Name", size = 0.7)
```

```{r}
regions %>%
  sf::st_drop_geometry() %>%
  select(Name, Level, url) %>% 
  arrange(Name) %>% 
  DT::datatable(escape = -4)
```

```{r, eval=FALSE}

sample_to_build_regex = "west of|west y|hereford|nott|leic|manc|liv|cam"
region_names_to_build = regions %>% 
  filter(grepl(pattern = sample_to_build_regex, x = Name, ignore.case = TRUE)) %>% 
  pull(Name)

dn = dn # dirctory name
dir.create(dn)
# region_names_to_build = c("West Yorkshire", "Nottingham")
rmarkdown::render("code/index.Rmd", output_dir = dn)
# region_names_to_build = c("Greater London", "Cambridgeshire")

rn = "West of England"
for(rn in region_names_to_build) {
  region = regions %>% filter(Name == rn)
  t = Sys.time()
  message("Building for ", rn)
  d = file.path(dn, region$html_name)
  dir.create(d)
  region_name = region$Name
  # source("code/build.R")
  rmarkdown::render(input = "code/build.R", output_dir = d, knit_root_dir = ".")
  plot(sf::st_geometry(r_lanes_top))
  htmlwidgets::saveWidget(m_leaflet, file.path("~/cyipt/tempCycleways/", d, "m.html"))
  time_to_run = Sys.time() - t
  rmarkdown::render("code/region_index.Rmd", output_file = file.path("~/cyipt/tempCycleways/", d, "index.html"))
  message(round(time_to_run), " minutes to build ", rn)
}
```

### 2020-05-28 code/region_index.Rmd
Add per region landing page

---
title: "Rapid cycleway prioritisation tool"
author: "University of Leeds"
output: html_document
---

@@

```{r, eval=FALSE}
# test build works before running for all:
source("code/build.R")
```

```{r}
regions = readRDS("regions_dft.Rds")
regions_centroids = sf::st_point_on_surface(regions)
regions$html_name = tolower(gsub(pattern = " |, ", replacement = "-", regions$Name))
regions$url = paste0("<a href='", regions$html_name ,"' target='_blank'>", regions$Name, "</a>")
```

```{r}
pvars = c("Name", "Level")
tm_shape(regions) + tm_polygons("Level", popup.vars = pvars) + tm_shape(regions_centroids) + tm_text("Name", size = 0.7)
```

```{r}
regions %>%
  sf::st_drop_geometry() %>%
  select(Name, Level, url) %>% 
  arrange(Name) %>% 
  DT::datatable(escape = -4)
```

```{r, eval=FALSE}

sample_to_build_regex = "west of|west y|hereford|nott|leic|manc|liv|cam"
region_names_to_build = regions %>% 
  filter(grepl(pattern = sample_to_build_regex, x = Name, ignore.case = TRUE)) %>% 
  pull(Name)

dn = dn # dirctory name
dir.create(dn)
# region_names_to_build = c("West Yorkshire", "Nottingham")
rmarkdown::render("code/index.Rmd", output_dir = dn)
# region_names_to_build = c("Greater London", "Cambridgeshire")

rn = "West of England"
for(rn in region_names_to_build) {
  region = regions %>% filter(Name == rn)
  t = Sys.time()
  message("Building for ", rn)
  d = file.path(dn, region$html_name)
  dir.create(d)
  region_name = region$Name
  # source("code/build.R")
  rmarkdown::render(input = "code/build.R", output_dir = d, knit_root_dir = ".")
  plot(sf::st_geometry(r_lanes_top))
  htmlwidgets::saveWidget(m_leaflet, file.path("~/cyipt/tempCycleways/", d, "m.html"))
  time_to_run = Sys.time() - t
  rmarkdown::render("code/region_index.Rmd", output_file = file.path("~/cyipt/tempCycleways/", d, "index.html"))
  message(round(time_to_run), " minutes to build ", rn)
}
```

>>>>

---
output: html_document
title: '`r region$Name`'
---

@@

```{r}
knitr::include_url("m.html")
```

See full map [here](m.html).

```{r}
DT::datatable(res_table)
```
